Predicting which anime are animazing through quantitative analysis

### 2024-04-14 paper/paper.qmd
Minor improvements. Abstract and title draft.

---
title: "Animazing"
subtitle: "What was found"
author: Allen Uy
thanks: "Code and data are available at: https://github.com/varygx/AnimeAnalysis"
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

Anime refers to animation originating from Japan. In 2021, half of Netflix's 222 million subscribers watched some anime on the platform and viewership saw an increase of 20% in the total hours over the previous year [@netflixAnime].

MyAnimeList, herein referred to as MAL, is one of the largest and most popular anime database and communities online. Users are able to keep track of anime they have watched or plan to, as well as rate and find similar anime.

The estimand of interest is...

@@

The MAL API is capable of fetching up to 500 anime based on ranking at a time for a given offset. @tbl-anime_dataset shows a small subset of the data gathered. Relatively little cleaning was required as the API allows one to specify what fields should be returned. The genre was returned as a list of strings which was turned into a multi-hot encoding for data processing. MAL has 74 listed genres and themes, so only 2 genre columns are displayed here for readability.

@@

# analysis_data <- clean_anime

@@

@@

>>>>

---
title: "Predicting which anime are animazing through quantitative analysis"
subtitle: "People are more likely to rate great anime, regardless of age"
author: Allen Uy
thanks: "Code and data are available at: https://github.com/varygx/AnimeAnalysis"
date: today
date-format: long
abstract: "This paper examines the top 10000 anime on MyAnimeList (MAL) by user score to understand the tendencies of highly rated anime. Using data provided by the MAL API, we discovered that the fraction of users that rate an anime to the total users that have engaged with the anime is a large indicator of user score. Our multiple linear regression model predicts the user score of an anime based on scoring fraction, date, and popularity and may indicate highly rated anime that have not yet gotten adequate exposure based on difference between the predicted and actual scores. This concept of scoring fraction is applicable to media forms beyond anime and may serve as the basis for recommendation algorithms."
format: pdf
number-sections: true
bibliography: references.bib
keywords: anime, regression, MyAnimeList
---

@@

Anime refers to animation originating from Japan. (I want to introduce what anime is better). In 2021, half of Netflix's 222 million subscribers watched some anime on the platform and viewership saw an increase of 20% in the total hours over the previous year [@netflixAnime]. Anime is not much different compared to other forms of media, however anime and animation in general is still often regarded by many as 'childish', despite plenty of anime covering serious topics[@enjoyAnimation].

MyAnimeList, herein referred to as MAL, is one of the largest and most popular anime databases and communities online. Users are able to keep track of anime they have watched or plan to watch, as well as rate and find similar anime. MAL is similar to IMDb in terms of functionality.

The estimand of interest is the effect of

@@

The MAL API is capable of fetching up to 500 anime based on ranking at a time for a given offset. @tbl-anime_dataset shows a small subset of the data gathered. Relatively little cleaning was required as the API allows one to specify what fields should be returned. The genre was returned as a list of strings which was turned into a multi-hot encoding for data processing. MAL has 74 listed genres and themes, so only 2 genre columns are displayed here for readability. The fraction column was calculated as the fraction of num_scoring_users to num_list_users, this is the fraction of users that gave a score to the anime. The days_since_start column was calculated as the integer day difference between the start date of the anime and the date the dataset was gathered.

@@

@@

Maybe don't keep this

@@

# Datasheet

Link to datasheet in repo here

# R package

TODO: create package
